---
title: "enrollment visualization for new pipeline"
author: "Bria Long"
date: "2024-10-25"
output: html_document
---

# Setup
```{r}
library(tidyverse)
library(here)
library(googlesheets4)
library(lubridate)
```

# Load family demographics, IDENTIFIABLE (!) with birthdate
```{r}
# I don't have the correct permsissions to do this somehow, reading in manually
# 
# families <- read_sheet('https://docs.google.com/file/d/1EbozDZBPTlaV6Sv9Eeho0CkcVhH6JvsT/edit?filetype=msexcel')
```

```{r}
families = read_csv(file=here::here('data/BabyView Demographic Sheet.csv')) %>%
  select(sid, date_birth, ethnicity, gender, parent_ed) %>%
  rename(subject_id = sid) %>%
  filter(!is.na(subject_id))
```

```{r}
families_deidentified <- families %>%
  select(subject_id, date_birth) %>%
  mutate(date_birth = mdy(date_birth)) %>%
  mutate(birthdate_short = round_date(date_birth, unit="month")) %>%
select(-date_birth)

write_csv(families_deidentified, file='subids_deidentified.csv')
```

# Load session tracking data
```{R}
# ongoing data collection
ongoing_session_durations <- read_sheet('https://docs.google.com/spreadsheets/d/1mAti9dBNUqgNQQIIsnPb5Hu59ovKCUh9LSYOcQvzt2U/edit?gid=754020357#gid=754020357',sheet='Ongoing_data_collection'
) %>%
  select(-Time, -Notes) %>% # causing join errors because incompatible types
  left_join(families, by=c('subject_id')) %>%
  mutate(cohort = 'ongoing')

```

```{r}
# release 1
release_1_session_durations <- read_sheet('https://docs.google.com/spreadsheets/d/1mAti9dBNUqgNQQIIsnPb5Hu59ovKCUh9LSYOcQvzt2U/edit?gid=1883822719#gid=1883822719', sheet='Main_Release_1_Corrected') %>%
  select(-Time, -Notes) %>%
  left_join(families, by=c('subject_id')) %>%
  mutate(cohort = 'release_1')
```

```{r}
all_session_durations <- release_1_session_durations %>%
  full_join(ongoing_session_durations) %>%
  filter(!is.na(Date)) %>%
  filter(map_lgl(Date, ~ !is.null(.x)))  %>%
  mutate(date_column = map_chr(Date, ~ as.character(.x[1])))  %>%
  filter(date_column!='NA') %>%
  mutate(date_tested = ymd(date_column)) 
  
```


```{r}
##
seconds_recorded_first_release = sum(release_1_session_durations$Duration, na.rm=TRUE)
hours_recorded_first_release = (seconds_recorded_first_release/60)/60
##
unprocessed_videos = sum(is.na(release_1_session_durations$Duration))
```

In the first BV-main release, we have `r hours_recorded_first_release` processed hours, and `r unprocessed_videos` unprocessed videos (maybe mismatched in some way).

```{r}
##
seconds_recorded_ongoing = sum(ongoing_session_durations$Duration, na.rm=TRUE)
hours_recorded_ongoing = (seconds_recorded_ongoing/60)/60
##
unprocessed_videos = sum(is.na(ongoing_session_durations$Duration))
```

In the ongoing data collection pipeline, we have `r hours_recorded_ongoing` processed hours, and `r unprocessed_videos` unprocessed videos.


```{r}
blackout_to_dos = sum(!is.na(all_session_durations$`Blackout Portions`))
```
All together, this makes `r hours_recorded_ongoing+hours_recorded_first_release` hours of video, with `r blackout_to_dos` videos that have some portion redacted, and `length(all_session_durations$video_id)` videos total.

# Wrangle data for plot
Look at number of hours by each subject
```{r}

library(knitr)
hours_by_subject <- all_session_durations %>% 
  group_by(subject_id) %>%
  summarize(num_hours = (sum(Duration, na.rm=TRUE)/60)/60) %>%
  arrange(-num_hours) 
```

```{r}
main_plot_temp <- all_session_durations %>%
  filter(!is.na(Processed_date)) %>%
  filter(!is.na(Duration)) %>%
  rowwise() %>%
  mutate(age_in_days_during_video = as.numeric(difftime(ymd(date_tested), mdy(date_birth), units='days'))) %>%
  filter(age_in_days_during_video>0) %>%
  filter(!age_in_days_during_video>10000) %>% # some years = 2204
  mutate(age_in_months_during_video = age_in_days_during_video/30.44)
```

```{r}
# what <- main_plot_temp %>%
  # filter(age_in_days_during_video>10000)
```

```{r}
by_subject <- main_plot_temp %>%
  group_by(subject_id, ethnicity, gender, parent_ed) %>%
  summarize(total_recorded = (sum(Duration, na.rm=TRUE)/60)/60)
```

1

```{R}
hist(main_plot_temp$age_in_days_during_video)
```

```{r}
hist(main_plot_temp$age_in_months_during_video)
```

```{r}
main_plot_age_bin <- main_plot_temp %>%
  filter(!is.na(age_in_months_during_video)) %>%
  filter(!is.na(Duration)) %>%
  mutate(duration_in_minutes = sum(Duration)/60) %>%
  group_by(subject_id) %>%
  arrange(age_in_days_during_video) %>%
  mutate(minutes_cumulative = cumsum(duration_in_minutes)) %>%
  select(subject_id, minutes_cumulative, age_in_days_during_video, ethnicity, gender, parent_ed)
```

```{r}
check <- main_plot_temp %>%
  filter(!is.na(Duration)) %>%
  group_by(subject_id) %>%
  summarize(hours = (sum(Duration)/60)/60)

sum(check$hours) # 715 hours
```

# Main plot of age by duratino
```{r}
ggplot(main_plot_age_bin, aes(x=age_in_days_during_video/30.44, y=minutes_cumulative/60, col=subject_id)) +
  geom_point(alpha=.6, size=.5) +
  theme(legend.position='right') +
  ylab('Cumulative hours of videos') +
  xlab('Age (in months) during recording')  +
  theme(legend.position = 'none') +
  xlim(0,36)
  # geom_line(aes(group=subject_id)) +
  # facet_wrap(~subject_id)

# ggsave('age_by_duration.pdf', width=4, units='in')
```


```{r}
ggplot(main_plot_age_bin, aes(x=age_in_days_during_video/30.44, y=minutes_cumulative/60, col=subject_id)) +
  geom_point(alpha=.6, size=.5) +
  theme(legend.position='right') +
  ylab('Cumulative hours of videos') +
  xlab('Age (in months) during recording')  +
  theme(legend.position = 'none') +
  geom_line(aes(group=subject_id)) +
  facet_wrap(~ethnicity)
```
```{r}
ggplot(main_plot_age_bin, aes(x=age_in_days_during_video/30.44, y=minutes_cumulative/60, col=subject_id)) +
  geom_point(alpha=.6, size=.5) +
  theme(legend.position='right') +
  ylab('Cumulative hours of videos') +
  xlab('Age (in months) during recording')  +
  theme(legend.position = 'none') +
  geom_line(aes(group=subject_id)) +
  facet_wrap(~gender)
```

```{r}
ggplot(main_plot_age_bin, aes(x=age_in_days_during_video/30.44, y=minutes_cumulative/60, col=subject_id)) +
  geom_point(alpha=.6, size=.5) +
  theme(legend.position='right') +
  ylab('Cumulative hours of videos') +
  xlab('Age (in months) during recording')  +
  theme(legend.position = 'none') +
  geom_line(aes(group=subject_id)) +
  facet_wrap(~ethnicity)
```

```{r}
ggplot(main_plot_age_bin, aes(x=age_in_days_during_video/30.44, y=minutes_cumulative/60, col=subject_id)) +
  geom_point(alpha=.6, size=.5) +
  theme(legend.position='right') +
  ylab('Cumulative hours of videos') +
  xlab('Age (in months) during recording')  +
  theme(legend.position = 'none') +
  geom_line(aes(group=subject_id)) +
  facet_wrap(~parent_ed)
```